Conversations in time: interactive visualisation to explore structured temporal data

### 2020-09-09 tsibbletalk.Rmd
minor tweaks

* {cranvas} and {cranvastime}
* [crossfilter.js](http://crossfilter.github.io/crossfilter/) & [dc.js](https://dc-js.github.io/dc.js/)
* {crosstalk} and html widgets
* {rJava}, {rbokeh} {loon}

@@

The city of Melbourne has sensors installed to count hourly tallies of pedestrians in order to capture downtown daily rhythms (cite). Figure \ref{fig:wrap-ped} shows the first five months of 2020 foot traffic at four locations, with the depiction of three pronounced slices in time. Figure \ref{fig:wrap-ped-1} unfolds all counts from January to May on their absolute time scales, facetted by four sensors. On March 16, Melbourne went to the stage three lockdown due to COVID-19, seeing a significant decline in traffic volume across the city. These lines are then folded into daily and weekly sections, shown as Figure \ref{fig:wrap-ped-2} and \ref{fig:wrap-ped-3} respectively. Seasonal variations have been popped out to viewers, complementing the not-just-magnitude-drop story. The pre-lockdown period is coloured with dark green and lockdown with orange.

@@

In response to the slider input, the plot will be updated and loaded with newly transformed data. Keeping the application as performant as possible is the top priority. Without completely redrawing the plot, the `plotly.js` react method is invoked internally. The underlying tsibble data is being called back and processed in R. Only transformed data gets fed back to the shiny server, along with reseting the x-axis ranges and breaks. The rest plot configurations, such as marks, y-axes, and layouts, are properly cached.

>>>>

* [crossfilter.js](http://crossfilter.github.io/crossfilter/) & [dc.js](https://dc-js.github.io/dc.js/)
* {cranvas} and {cranvastime}
* {crosstalk} and html widgets
* {rJava}, {rbokeh} {loon}

@@

The city of Melbourne has sensors installed to count hourly tallies of pedestrians in order to capture downtown daily rhythms (cite). Figure \ref{fig:wrap-ped} shows the first five months of 2020 foot traffic at four locations, with the depiction of three pronounced slices in time. Figure \ref{fig:wrap-ped-1} unfolds all counts from January to May on their absolute time line, facetted by four sensors. On March 16, Melbourne went to the stage three lockdown due to COVID-19, seeing a significant decline in traffic volume across the city. These lines are then folded into daily and weekly sections, shown as Figure \ref{fig:wrap-ped-2} and \ref{fig:wrap-ped-3} respectively. Seasonal variations have been popped out to viewers, complementing the not-just-magnitude-drop story. The pre-lockdown period is coloured with dark green and lockdown with orange.

@@

In response to the slider input, the plot will be updated and loaded with newly transformed data. At its core, keeping the application as performant as possible is the top priority. Without completely redrawing the plot, the `plotly.js` react method is invoked internally. The underlying tsibble data is being called back and processed in R. Only transformed data gets fed back to the shiny server, along with reseting the x-axis ranges and breaks. The rest plot configurations, such as marks, y-axes, and layouts, are properly cached.
